Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-10 paper.tex
Added more review responses

In order to judge which predictive modeling approach is applicable in
every case, we firstly have to consider the goal of a the model in a
cheminformatics setting. In some cases, pure predictive ability is
desired -- such as in a virtual screening setting. (Basically, only the
reliability of the model matters, but other aspects such as
interpretability are of minor importance.) For such cases, the
complexity of the modeling approach is immaterial, as it leads to
accurate and generalizable results. Here a large-scale mining capacity
is crucial. On the other hand, when working with chemists and
biologists, the interpretability of a model and risk reduction
arguments are paramount, since we have to translate better-predicted
\emph{in silico} compounds into real-world compounds. In such cases,
``black-box methods'' can be less useful, though attempts have been
made to interpret vectorial models built using neural networks,
Support Vector Machines or random forests as well.

>>>>

In order to judge which predictive modeling approach is applicable in
every case, we firstly have to consider the goal of a the model in a
cheminformatics setting. In some cases, pure predictive ability is
desired -- such as in a virtual screening setting. (Basically, only
the reliability of the model matters, but other aspects such as
interpretability are of minor importance.) For such cases, the
complexity of the modeling approach is immaterial, as it leads to
accurate and generalizable results. Here a large-scale mining capacity
is crucial. On the other hand, when working with chemists and
biologists, the interpretability of a model and risk reduction
arguments are paramount, since we have to translate better-predicted
\emph{in silico} compounds into real-world compounds. In such cases,
``black-box methods'' can be less useful, though attempts have been
made to interpret vectorial models built using neural networks,
na\"{i}ve Bayes, Support Vector Machines or random forests as well.
